Technology-based aids for people affected by Autism Spectrum Disorder (ASD)

### 2017-12-07 paper.tex
Approvate le conclusioni

Moreover, although normally it is not considered as a diagnostic criteria, motor impairment associated with ASD may have a significant impact on daily life tasks and, since up to 80\% of children with autism show motor anomalies highly correlated with the severity of social deficiency, hand-eye coordination could be considered as a new early diagnostic strategy for ASD syndrome \DP{Ho tolto la reference al primo paper, mi sembrava ridondante}. In fact, it has been suggested that sensory integration with bad timing brings to poor motor performance in children with ASD: the task of integrating multisensory input influences the forming of coherent perception, action coordination and planning. Nowadays, the normal procedure to assess this motor coordination deficiency is the clinical observation and self-report questionnaires, so a new non-invasive objective method to map the development of ASD such hand-eye motor performance, could be a powerful diagnostic tool.

@@

Looking at the whole system it can be stated that this tool can allow a very useful didactic training procedure for people with \gls{asd}, and its potential affordability for normal families and relatively easy use make it a powerful solution in the research field  of \gls{asd}. \cri{forse devo essere più specifica nella parte in cui descrivo come il sistema as adatta le task all'ansia?}
\DP{No secondo me quando hai spiegato che il sistema si adatta all'ansia e come rileva l'ansia, siamo apposto! Come hai fatto tu va benissimo!}

\section{Conclusions}\label{sec:conclusions}
All the presented experiments had reach good results while applied to subjects with \gls{asd}. This proofs that new technologies can be used, together with a specialized therapist, in the medical fields to prognosticate or manage the \gls{asd}.

Unfortunately, before these tools are normally used in clinics and hospitals, it must takes a non-negligible amount of time and a lot of tests, but in a \textit{not-so-far} future, these techniques can help us to improve the life of the people affected by \gls{asd} and maybe they will allow us a better understanding of this desease.

>>>>

Moreover, although normally it is not considered as a diagnostic criteria, motor impairment associated with ASD may have a significant impact on daily life tasks and, since up to 80\% of children with autism show motor anomalies highly correlated with the severity of social deficiency, hand-eye coordination could be considered as a new early diagnostic strategy for ASD syndrome. In fact, it has been suggested that sensory integration with bad timing brings to poor motor performance in children with ASD: the task of integrating multisensory input influences the forming of coherent perception, action coordination and planning. Nowadays, the normal procedure to assess this motor coordination deficiency is the clinical observation and self-report questionnaires, so a new non-invasive objective method to map the development of ASD such hand-eye motor performance, could be a powerful diagnostic tool.

@@

Looking at the whole system it can be stated that this tool can allow a very useful didactic training procedure for people with \gls{asd}, and its potential affordability for normal families and relatively easy use make it a powerful solution in the research field  of \gls{asd}.

\section{Conclusions}\label{sec:conclusions}
All the presented experiments reached good results while applied to subjects with \gls{asd}: they prove that new technologies, together with a specialized therapist, can be used in the medical field to diagnose or manage the \gls{asd}.

Unfortunately, it takes a non-negligible amount of time and several tests before these tools can be normally used in clinics and hospitals and the path is still long, but in a \textit{not-so-far} future these techniques will be able to help us improve the life of the people affected by \gls{asd} and maybe better understand this disease.
